Making Sequential Programs Deterministic

### 2019-04-03 design.tex
Added closing bracket

    \caption{Improving precision}
\todo{In the \rulename{map precision} rule, should the \<Det> in the
  conclusion be $\beta_v$?}
    \label{fig-precision-rules}
\end{figure}
According to this rule, if the \<Set> receiver has type \codeid{@OrderNonDet Set<@Det List} and the argument to the \codeid{equals()} method is
also of the same type, the return type gets the qualifier \<Det>. Without this precision rule, the return type would have been instantiated as \<NonDet> which
is sound but imprecise. This rule is careful enough to not annotate the return type of \<equals()> as \<Det> if a type argument to either the
receiver or the argument happens to be an \codeid{OrderNonDet List}.
\todo{The following is the key!  Put in earlier.}(An order nondeterministic list does not provide any guarantee on the
equality as it is dependent on the iteration order).

>>>>

    \caption{Improving precision}
\todo{In the \rulename{map precision} rule, should the \<Det> in the
  conclusion be $\beta_v$?}
    \label{fig-precision-rules}
\end{figure}
According to this rule, if the \<Set> receiver has type \codeid{@OrderNonDet Set<@Det List>} and the argument to the \codeid{equals()} method is
also of the same type, the return type gets the qualifier \<Det>. Without this precision rule, the return type would have been instantiated as \<NonDet> which
is sound but imprecise. This rule is careful enough to not annotate the return type of \<equals()> as \<Det> if a type argument to either the
receiver or the argument happens to be an \codeid{OrderNonDet List}.
\todo{The following is the key!  Put in earlier.}(An order nondeterministic list does not provide any guarantee on the
equality as it is dependent on the iteration order).
